\begin{acknowledgements}

First and foremost, I must thank my advisor, Professor Irene A. Chen. I still don't know why she took a chance on a bright-eyed, bushy-tailed graduate student with absolutely no background in microbial ecology or bioinformatics, but I will be forever grateful that she did. Her guidance, support, patience, and countless insights (scientific and otherwise) were instrumental in my professional and personal development. Irene gave me the opportunities, responsibilities, and mentorship that allowed me to become the scientist I always hoped I could be; thank you so much, Irene.

I owe a great deal of gratitude to the collaborators, advisors, and colleagues who I have had the good fortune of working with over the years. My dissertation work would not be possible without Dr. John Deacon, Professor Juhee Lee, Yuning Shen, and Colin Kim; thank you for your tireless efforts. To my thesis committee, Professors Cherie Briggs and Ambuj Singh, thank you for keeping me on track and holding me accountable; your guidance inspired me every step of the way. Thank you to the administrative staff, for always offering a helping hand: Stella Hahn, Nicole Becker, Lauren Baker, Adrian Shelor, Cabe Fletcher, Trevor Bellefeuille, Jamie Bishop, Jen Smith, and Rob Callaway. Thank you to my fellow Chen Labbers: Celia Blanco, Ranajay Saha, Huan Peng, Jennifer Mobberley, Yei-Chen Lai, Abe Pressman, Greg Campbell, Baoqing Zhou, Evan Janzen, Claire Tran, Yuning Shen, Josh Kenchel, Ray Borg, and Damayanti Bagchi. I am very lucky to count myself among you.

And finally, I must thank my family and friends for their endless love and support. They say scientific progress is rooted in failure; that may be even more true when \textit{learning} to do science in graduate school. I'm so grateful that, in all my failures and triumphs, you were there to keep my feet on the ground. Thank you all so very much.

\end{acknowledgements} 