\begin{vitae}
\addcontentsline{toc}{chapter}{Curriculum Vitae}

\begin{vitaesection}{Education}
\vspace{-0.1cm}
\item [2015-2020]	Ph.D. in Biochemistry and Molecular Biology (Expected), University of California, Santa Barbara.
\item [2011-2015]	B.A. in Biochemistry, Vassar College.
\end{vitaesection}

\begin{vitaesection}{Honors and Awards}
\item[2020]	BMSE Symposium Poster Award - Best Microbiology Poster
\end{vitaesection}

\begin{vitaesection}{Teaching Experience}
\item [2015]	MCDB1AL (Intro Biology Lab) Teaching Assistant
\end{vitaesection}

\textbf{Publications}
\begin{itemize}
\item \textbf{Verbanic, S.}, Shen, Y., Lee, J., Deacon, J. M., \& Chen, I. A. (2020) Microbial predictors of healing and short-term effect of debridement on the microbiome of chronic wounds: the role of facultative anaerobes. \textit{npj Biofilms \& Microbiomes; accepted} 

\item Blanco, C., \textbf{Verbanic, S.}, Seelig, B., \& Chen, I. A. (2020) High throughput sequencing of \textit{in vitro} selection for proteins using mRNA display. \textit{Phys Chem Chem Phys; accepted}

\item \textbf{Verbanic, S.}, Kim, C. Y., Deacon, J. M. \& Chen, I. A. (2019) Improved single-swab sample preparation for recovering bacterial and phage DNA from human skin and wound microbiomes. \textit{BMC Microbiol} 19, 214

\item Saha, R., \textbf{Verbanic, S.} \& Chen, I. A. (2018) Lipid vesicles chaperone an encapsulated RNA aptamer. \textit{Nat Commun} 9, 2313

\item \textbf{Verbanic, S.}, Brady, O., Sanda, A., Gustafson, C., \& Donhauser, Z. J. (2014) A Novel General Chemistry Laboratory: Creation of Biomimetic Superhydrophobic Surfaces through Replica Molding. \textit{J Chem Educ} 91, 1477
\end{itemize}

\textbf{In Review}
\begin{itemize}
%\item Blanco, C., \textbf{Verbanic, S.}, Seelig, B., \& Chen, I. A. (2020) EasyDIVER: a pipeline for assembling and counting high throughput sequencing data from in vitro evolution of nucleic acids or peptides. \textit{Bioinformatics; in review}

\item Shuler, K., \textbf{Verbanic, S.}, Chen, I. A., \& Lee, J. (2020) A Bayesian Nonparametric Analysis for Zero Inflated Multivariate Count Data with Application to Microbiome Study. \textit{J Royal Stat Soc; in review}

%\item Shuler, K., \textbf{Verbanic, S.}, Chen, I. A., \& Lee, J. (2020) Bayesian Graphical Modeling of Microbial Community Composition. \textit{in preparation}
\end{itemize}

\textbf{Patents}
\begin{itemize}
\item Peng, H., \textbf{Verbanic, S.}, \& Chen, I. A. (2018) Targeted Gold Nanoparticles for Detection and Cell Killing in Bacterial Infections. \textit{USPTO, provisional patent}
\end{itemize}



\end{vitae}